test_for_p.values

### 2019-05-10 doc/strain_reports/CAROLI_Report.Rmd
moved files around to clean up

---
title: "AST_Report"
author: "April Peterson"
date: "January 4, 2019"
output: html_document
---

```{r setup, include=FALSE}
library(plyr)
library(dplyr)

@@

mouse_list = read.csv("~./MLH1repo/data/MLH1q_AST.csv", header=TRUE )
# this is the list of total mice
#load big MLH1 Rdata file

@@

#don't go row by row, for each mouse, 
#summarize the whole dataset...
#make new dataframe
mouse.report <- data.frame("total.Nmice" = length(unique(mouse_list$mouse)), 
      "Nmales"= length(mouse_list$mouse[mouse_list$sex == "male"]),
      "Nfemales"= length(mouse_list$mouse[mouse_list$sex == "female"]),
      "passed.mice" = sum( mouse_list$mouse  %in%  MLH1_data$mouse)

     )
#imaged mice...

@@

>>>>

---
title: "CAROLI Report"
author: "April Peterson"
date: "December 12, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
library(plyr)
library(dplyr)
library(ggplot2)

@@

mouse_list = read.csv("~./MLH1repo/data/MLH1q_CAROLI.csv", header=TRUE )
# this is the list of total mice
#load big MLH1 Rdata file

@@

#don't go row by row, for each mouse, 
#summarize the whole dataset...
#make new dataframe
mouse.report <- data.frame("total.Nmice" = length(unique(mouse_list$mouse)), 
      "Nmales"= length(mouse_list$mouse[mouse_list$sex == "male"]),
      "Nfemales"= length(mouse_list$mouse[mouse_list$sex == "female"]),
      "passed.mice" = sum( mouse_list$mouse  %in%  MLH1_data$mouse),

      #length of $M.stained without staining in it
      "Non.Stained.mice" = sum( mouse_list$mouse  %in%  MLH1_data$mouse),
      #length of $quant.batch without Batch in it
      "Non.Qunt.mice" = sum( mouse_list$mouse  %in%  MLH1_data$mouse)

     )
#number of unquant'd mice
#number of unstained mice

#imaged mice...

@@

```{r}
#MAKE HISTOGRAM OF THE AGES 
Ages_hist <- ggplot(data= mouse_list, aes(age.weeks))+geom_histogram()+facet_wrap(~sex)

```{r}
#merge DOB from ALP metdata sheet?
```

### 2019-05-10 doc/strain_reports/KAZ_Report.Rmd
moved files around to clean up

---
title: "AST_Report"
author: "April Peterson"
date: "January 4, 2019"
output: html_document
---

@@

#input
#output: Rmd file that can be read on github

@@

mouse_list = read.csv("~./MLH1repo/data/MLH1q_AST.csv", header=TRUE )
# this is the list of total mice
#load big MLH1 Rdata file

#format the dates into standard format
mouse_list$DOB <- as.Date(mouse_list$DOB,format='%m/%d/%Y')

setwd("C:/Users/alpeterson7/Documents/MLH1repo/")
source("~./MLH1repo/src/CommonFunc.R")#this works
#source("src/Func_addCategory.R")

@@

#ages in days -- 
#5 to 15 weeks
#35 days,  105days

#don't go row by row, for each mouse, 
#summarize the whole dataset...
#make new dataframe
mouse.report <- data.frame("total.Nmice" = length(unique(mouse_list$mouse)), 
      "Nmales"= length(mouse_list$mouse[mouse_list$sex == "male"]),
      "Nfemales"= length(mouse_list$mouse[mouse_list$sex == "female"]),
      "passed.mice" = sum( mouse_list$mouse  %in%  MLH1_data$mouse)

     )
#imaged mice...

@@

>>>>

---
title: "TOM_Report"
author: "April Peterson"
date: "January 4, 2019"
output: pdf_document
---

@@

@@

mouse_list = read.csv("~./MLH1repo/data/MLH1q_KAZ.csv", header=TRUE )
# this is the list of total mice
#load big MLH1 Rdata file
#format the dates into standard format
mouse_list$DOB <- as.Date(mouse_list$DOB,format='%m/%d/%Y')
#check that the header is the same

source("~./MLH1repo/src/CommonFunc.R")
#source("src/Func_addCategory.R")

@@

#merge 
#mouse_list

smllmergedDF = merge(MLH1_data, mouse_list, by = "mouse")
#these are all cell level obsers

#compare the number of images across reports .... total.image ... good.images
mouse.comparison <- ddply(mouse_list, c("mouse"), summarise,

                          Nmice = length(unique(mouse)),
                         #give the value from the AP_mouse table
                         nQunt.images = AP_mouse_table$Ncells[which(AP_mouse_table$mouse == mouse)]

            )

#don't go row by row, for each mouse, 
#summarize the whole dataset...
#make new dataframe
mouse.report <- data.frame("total.Nmice" = length(unique(mouse_list$mouse)), 
      "Nmales"= length(mouse_list$mouse[mouse_list$sex == "male"]),

      "passed.mice.m" = sum( mouse_list$mouse[mouse_list$sex == "male"]  %in%  MLH1_data$mouse),

      "Nfemales"= length(mouse_list$mouse[mouse_list$sex == "female"]),

      "passed.mice.f" = sum( mouse_list$mouse[mouse_list$sex == "female"]  %in%  MLH1_data$mouse)

     )
#imaged mice...
#fill in number of images from MLH1,
#unquant
#unstained
#non-imaged

@@

```{r}
#MAKE HISTOGRAM OF THE AGES 
Ages_hist <- ggplot(data= mouse_list, aes(age.weeks))+geom_histogram()+facet_wrap(~sex)
#not sure if histograms are the best

### 2019-05-10 draft_scripts/test4pvalues.Rmd
moved files around to clean up

outlist15 = list()
for(fif in 1:length(unique(twenty$mouse))){
  print(twenty$mouse[fif])
  #
  mus_data <- twenty_data[twenty_data$mouse == twenty$mouse[fif],]

@@

plot_list20 = list()
for (i in 1:length(twenty$mouse)){
  print(i)  
  try_df <- as.data.frame(outlist20[[i]])
  colnames(try_df) <- "pvals"
  Title_mus_name <- paste("1000 iterations\n, Test of 2 Samples of 20, \n", names(outlist20[i]) )
  p20 <- ggplot(try_df) + ggtitle( Title_mus_name ) + xlim(0,1)+
        geom_histogram(aes(x=pvals) )#xlim
    plot_list20[[i]] <- p20
}

plot_list10 = list()
for (i in 1:length(twenty$mouse)){
  print(i)  
  try_df <- as.data.frame(outlist10[[i]])
  Title_mus_name <- paste("1000 iterations\n Test of 2 Samples of 10, \n", names(outlist10[i]) )
  colnames(try_df) <- "pvals"
  p10 <- ggplot(try_df) + ggtitle( Title_mus_name ) +xlim(0,1)+
        geom_histogram(aes(x=pvals) )#xlim
  #tryfiting 3 plots

@@

plot_list15 = list()
for (i in 1:length(twenty$mouse)){
  print(i)  
  try_df <- as.data.frame(outlist15[[i]])
  Title_mus_name <- paste("1000 iterations\n Test of 2 Samples of 15, \n", names(outlist15[i]) )
  colnames(try_df) <- "pvals"
  p15 <- ggplot(try_df) + ggtitle( Title_mus_name ) + xlim(0,1)+
        geom_histogram(aes(x=pvals) )#xlim
  #tryfiting 3 plots
    plot_list15[[i]] <- p15
}

>>>>

outlist15 = list()
for(fif in 1:length(unique(twenty$mouse))){
  print(twenty$mouse[fif])
  mus_data <- twenty_data[twenty_data$mouse == twenty$mouse[fif],]  #mus data is the mouse specific data

@@

#list for n=20 sample simulations
plot_list20 = list()
for (i in 1:length(twenty$mouse)){
  print(i)  
  try_df <- as.data.frame(outlist20[[i]])
  colnames(try_df) <- "pvals"
  Title_mus_name <- paste("1000 iterations\n, Test of 2 Samples of 20, \n", names(outlist20[i]) )
  p20 <- ggplot(try_df) + ggtitle( Title_mus_name ) + xlim(0,1)+
        geom_histogram(aes(x=pvals) )#xlim
    plot_list20[[i]] <- p20
}

#list for n=10 sample simulations
plot_list10 = list()
for (i in 1:length(twenty$mouse)){
  print(i)  
  try_df <- as.data.frame(outlist10[[i]])
  Title_mus_name <- paste("1000 iterations\n Test of 2 Samples of 10, \n", names(outlist10[i]) )
  colnames(try_df) <- "pvals"
  p10 <- ggplot(try_df) + ggtitle( Title_mus_name ) +xlim(0,1)+
        geom_histogram(aes(x=pvals) )#xlim
  #tryfiting 3 plots

@@

#list for n=15 sample simulations
plot_list15 = list()
for (i in 1:length(twenty$mouse)){
  print(i)  
  try_df <- as.data.frame(outlist15[[i]])
  Title_mus_name <- paste("1000 iterations\n Test of 2 Samples of 15, \n", names(outlist15[i]) )
  colnames(try_df) <- "pvals"
  p15 <- ggplot(try_df) + ggtitle( Title_mus_name ) + xlim(0,1)+
        geom_histogram(aes(x=pvals) )#xlim
  #tryfiting 3 plots
    plot_list15[[i]] <- p15
}
